Making Multiple Dice Work as One: CAD Flows and Routing Architectures for Silicon Interposer FPGAs

### 2014-12-09 doc/journal/fpgapaperfinal/FPGAPaper/fpga2014paper.tex
Changed title.
git-svn-id: https://vtr-verilog-to-routing.googlecode.com/svn/branches/javeed@4525 8e3573b8-cf2c-4f14-ef6d-137439e28b8b
Edits to effectiveness of placer enhancements.
git-svn-id: https://vtr-verilog-to-routing.googlecode.com/svn/branches/javeed@4526 8e3573b8-cf2c-4f14-ef6d-137439e28b8b

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
% Do not put math or special symbols in the title.
\title{CAD and Routing Architecture for Interposer-Based Multi-FPGA Systems}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%

\author{
		% 1st author
		Ehsan~Nasiri,
		% 2nd author
		Javeed~Shaikh,
		% 3rd author
		Andre~Hahn~Pereira,
		% 4th author
        and~Vaughn~Betz,~\IEEEmembership{Member,~IEEE,}%
\thanks{E. Nasiri is with Altera Corporation, Toronto Technology Center, Toronto, Ontario, Canada (email: enasiri@altera.com)}% 
\thanks{J. Shaikh is with Google, Mountain View, California, USA (email: jvds@google.com)}%
\thanks{A. H. Pereira is with the Computer and Digital Systems Engineering Department - Escola Polit\'{e}cnica, University of S\~{a}o Paulo, S\~{a}o Paulo, SP, Brazil (email: andre.hahn@usp.br)}%
\thanks{V. Betz is with the Department of Electrical and Computer Engineering, University of Toronto, Toronto, Ontario, Canada (email: vaughn@eecg.utoronto.ca)}%
\thanks{Manuscript received January 19, 2014.}}

@@

\subsubsection{Effectiveness of Placer Optimizations}
\label{sec:effectiveness_of_placer_enhancements}
Enabling the enhancements described in Section~\ref{cad_enh_placer_subsection} improves the minimum routable channel width and circuit speed. As shown in Figure~\ref{fig:comparison_minW}, for architectures with low \textit{\% wires cut} (high interposer capacity), the placer optimizations are only marginally beneficial compared to the original VPR placer since the interposer wires are not scarce; but as more wires are cut and we reach the realistic interposer capacity of commercial FPGAs, the placer optimizations provide higher and higher reduction in minimum channel width. When 80\% of wires are cut, the placer optimizations result in 11.3\% reduction in minimum channel width.

@@

The optimizations also help the placer to place related entities on the same die to reduce the number of inter-die signal crossings and hence increase circuit speed. At 80\% wires cut, the placer optimizations result in 8.4\% higher circuit speed.
\begin{figure}[!htbp]
\centering
\includegraphics[width=\linewidth]{placer_opt_fmax.eps}
\caption{Impact of placer optimizations on circuit speed.}
\label{fig:comparison_fmax}
\end{figure}

>>>>

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
% Do not put math or special symbols in the title.
\title{Making Multiple Dice Work as One: CAD Flows and Routing Architectures for Silicon Interposer FPGAs}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%

\author{
		% 1st author
		Ehsan~Nasiri,
		% 2nd author
		Javeed~Shaikh,
		% 3rd author
		Andre~Hahn~Pereira,
		% 4th author
        and~Vaughn~Betz,~\IEEEmembership{Member,~IEEE,}%
\thanks{E. Nasiri is with Altera Corporation, Toronto Technology Center, Toronto, Ontario, Canada (email: enasiri@altera.com)}% 
\thanks{J. Shaikh is with Google, Mountain View, California, USA (email: jvds@google.com)}%
\thanks{A. H. Pereira is with the Computer and Digital Systems Engineering Department - Escola Polit\'{e}cnica, University of S\~{a}o Paulo, S\~{a}o Paulo, SP, Brazil (email: andre.hahn@usp.br)}%
\thanks{V. Betz is with the Department of Electrical and Computer Engineering, University of Toronto, Toronto, Ontario, Canada (email: vaughn@eecg.utoronto.ca)}%
\thanks{Manuscript received December 19, 2014.}}

@@

\subsubsection{Effectiveness of Placer Optimizations}
\label{sec:effectiveness_of_placer_enhancements}
Enabling the enhancements described in Section~\ref{cad_enh_placer_subsection} improves both the minimum routable channel width and circuit speed. As shown in Figure~\ref{fig:comparison_minW}, for architectures with low \textit{\% wires cut} (high interposer capacity), the placer optimizations have only a marginal benefit on routability compared to the original VPR placer since the interposer wires are not scarce, but as more wires are cut and we reach the realistic interposer capacity of commercial FPGAs, the placer optimizations provide higher and higher reductions in minimum channel width. When 80\% of wires are cut, the placer optimizations result in 11.3\% reduction in minimum channel width.

@@

The optimizations also guide the placer to keep related entities on the same die to reduce the number of inter-die signal crossings and hence increase circuit speed. This speed improvement is fairly consistent across a wide range of \% wires cut, averaging 12.5\% higher circuit speed.
\begin{figure}[!htbp]
\centering
\includegraphics[width=\linewidth]{placer_opt_fmax.eps}
\caption{Impact of placer optimizations on circuit speed.}
\label{fig:comparison_fmax}
\end{figure}
